\documentclass[12pt]{amsart}
\usepackage{../marktext} 
%% Remove draft for real article, put twocolumn for two columns
\usepackage{../svmacro}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
%\usepackage{authblk}
\usepackage[style=alphabetic, backend=biber]{biblatex}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}

%% commentary bubble
\newcommand{\SV}[2][]{\sidenote[colback=green!10]{\textbf{SV\xspace #1:} #2}}

%% Title 
\title{ MATH 170 -- 601: Midterm 3 }
%\author[1]{Co-author}
\author{Good luck!}
%\affil[1]{Institute}
\date{}

\begin{document}


\maketitle

There are three questions. Make sure you justify all your work for complete credit.

\section*{Rules}

\begin{itemize}[leftmargin=*]
    \item You have 50 minutes to complete your work and 10 minutes to upload your work.
    \item Open notes (you can use your notes freely).
    \item No use of internet, textbooks, computer algebra systems, calculators. 
    \item No collaboration.
\end{itemize}

\section*{Questions}
Each sub-problem (a,b) is worth 10 points.

\begin{enumerate}[label=\arabic*.,itemsep=10pt, leftmargin=*]
    \item
    Consider the following graph
   \begin{equation*}
       \set[\Big]{\set{a,b,c,d,e,f,g,h,i,j,k,l}, \set{ab,ac,ad,bc,bd,cd,be,ef,eg,fg,gh,hi,hj,hk,hl,ij,ik,il,jk,jl,kl}}\,.
   \end{equation*}
   \begin{enumerate}
    \item Draw the graph. 
    \item Recall for a complete graph (all vertices are connected with each other by an edge) of $k$ vertices, $K_k$, $$P_{K_k}(n) = n(n-1)\dots(n-k+1)\,.$$ 
    Use the deletion-contraction formula to determine how many ways there are to color the above graph using 10 colors.
    \end{enumerate}
    \item 
        Consider a sample space of $7$ coin tosses.
        \begin{enumerate}
            \item What is the probability that the first and the last toss is the same?
            \item What is the probability that the last toss is head, given that the
                first toss is head?
        \end{enumerate}


    \item 
        \begin{enumerate}
            \item Compute the following:
                \begin{gather*}
                    \binom{1}{0} + \binom{1}{1} \,, \\
                    \binom{2}{0} + \binom{2}{1} + \binom{2}{2} \,, \\
                    \binom{3}{0} + \binom{3}{1} + \dots + \binom{3}{3} \,.
                \end{gather*}
    \item
        What should be the formula for 
        \begin{equation*}
            \binom{n}{0} + \binom{n}{1} + \dots + \binom{n}{n} \,.
        \end{equation*}

    \item[Bonus (5pts):] Prove the formula you just guessed.
        \end{enumerate}


\end{enumerate}



\end{document}
