\documentclass[12pt]{amsart}
\usepackage{amsaddr}
\usepackage{marktext} 
%% Remove draft for real article, put twocolumn for two columns
\usepackage{svmacro}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[style=alphabetic, backend=biber]{biblatex}
\addbibresource{bibliography.bib}

%% commentary bubble
\newcommand{\SV}[2][]{\sidenote[colback=green!10]{\textbf{SV\xspace #1:} #2}}

%% Title 
\title{ MATH 102: FINAL }
\author{Name:\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ ID: \_  \_  \_   \_  \_  \_  \_  \_ 
}

%\author{Co-author}
%\address{  }
%\email {  }
%
\date{Dec 3, 2023}

\begin{document}

\maketitle


There are 3 problems.

Make sure you justify all your work for complete credit.

\vspace{1cm}

SUBMITTED PROBLEMS: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

\vspace{3cm}
\section*{Rules}

\begin{itemize}[leftmargin=*]
	\item You have 80  minutes to complete your work..
	\item Closed books.
	\item No use of internet, textbooks, computer algebra systems, calculators.
	\item No collaboration.
	\item 1 person per bathroom break. When you go to the bathroom, turn in your cellphone and exam until return.
\end{itemize}

\begin{center}
	Good luck!
\end{center}

\newpage

\section*{Questions}

\begin{enumerate}[label=\arabic*.,itemsep=10pt, leftmargin=*]

	\item \textit{[60 points.]}
	      Translate the following into symbols, then negate the symbolic sentence, and translate the negation back to English.
	      \begin{enumerate}
		      \item Every natural number, when squared, remains a natural number.
		            \vspace{5cm}
		      \item Every real number has a cube root in the reals.
		            \vspace{5cm}
		      \item Not every integer has a square root in the reals.
		            \vspace{5cm}
		      \item There exists a smallest natural number.
		            \vspace{5cm}
		      \item There exists a largest negative integer.
		            \vspace{5cm}
		      \item Every real number, when multiplied by zero, equals zero.
	      \end{enumerate}

	      \newpage

	      \item\textit{[40 points.]}
	      \begin{enumerate}
		      \item \textit{[10 points.]}
		            Give a definition of function.
		            \vspace{7cm}

		      \item \textit{[10 points.]}
		            Give a definition of bijective function.
		            \vspace{7cm}
		      \item \textit{[10 points.]}
		            Give an example of a bijective function with both domain and co-domain to be $\R$.
		            \vspace{7cm}

		      \item \textit{[10 points.]}
		            Prove that the function you gave in the previous part is a bijection.
		            \vspace{7cm}


	      \end{enumerate}

	      \newpage

	\item \textit{[20 points.]} Prove by contradiction that if $A\cap C \subseteq B$ and $a \in C$, then
	      $a \not\in A \backslash B$.
	      \newpage


\end{enumerate}



\printbibliography
%\bibliography{refs}
%\bibliographystyle{halpha-abbrv}


\end{document}
