\documentclass[12pt]{amsart}
\usepackage{../marktext} 
%% Remove draft for real article, put twocolumn for two columns
\usepackage{../svmacro}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
%\usepackage{authblk}
\usepackage[style=alphabetic, backend=biber]{biblatex}
\usepackage{enumitem}

%% commentary bubble
\newcommand{\SV}[2][]{\sidenote[colback=green!10]{\textbf{SV\xspace #1:} #2}}

%% Title 
\title{ MATH 170: Topics for midterm 2 }
%\author[1]{Co-author}
\author{Good luck!}
%\affil[1]{Institute}
\date{}

\begin{document}


\maketitle


\section*{Rules}

\begin{itemize}
    \item The exam is on Nov 1 for Sections 1 and 601, and on Nov 2 for Section 2.
    \item Open notes (you can use your notes freely).
    \item No use of internet, textbooks, computer algebra systems, calculators. 
    \item No collaboration.
    \item The exam is during lecture and 50 minutes long.
    \item At the end of the exam, you will have 10 min to scan and upload your work to gradescope.
\end{itemize}


\section*{Scanning}

The easiest way to scan is to use the free version of the app ``Adobe Scan'' that is available for iPhone and Android.

\textbf{Before the midterm.} Download the app and try to use it at least once to create a pdf document out of 5 pages. E.g. scan your lecture notes.

\textbf{Using the app.} 
\begin{enumerate}
    \item Open the app.
    \item Allow it to access camera.
    \item Now the app should show you the camera and attempt to find a document.
    \item Move your camera so that the document you chose (lecture notes, shopping list, etc.) fits completely into the screen.
    \item The app will highlight the corners of the document with blue dots. Wait till the app makes the photo of the document (no need to press buttons). 
    \item Now the app will suggest you to drag the blue dots to adjust the corners of the document.
    \item Click ``Continue'' to return to the camera mode.
    \item Scan another page. Or if you are done, click the bottom right where you see the miniatures of the scans. You will then be able to review the pdf as it will appear in the file, reorder, crop or apply filters.
    \item When you are done reviewing, click ``Save PDF'' in the top right corner.
    \item Now you should see your document. Click ``Share'', choose ``Share a copy'', then choose any appropriate way of uploading the file to Gradescope. E.g. you can save the file to your file system and upload it from there, email it to yourself and use your laptop to upload, or come up with any other means of uploading the file to Gradescope.
    
\end{enumerate}



\section*{Advice}

\begin{itemize}
    \item {\bf Zeroth principle.}
On the day of the midterm, make sure that you have enough sleep (at least 7 hours), and don't forget to eat lunch and drink water beforehand -- your brain will thank you for taking care of it.   
    \item {\bf First principle.}
Make sure you learn how to present your work properly by looking
    at the solution / lecture notes for sample writings.
    Learning to have a style of your own is important.
    Going over solutions of homework is a good idea.
    \item Even though you are allowed to use your notes, prepare a cheat sheet with formulas for faster search during the midterm.

\end{itemize}




\section*{List of topics}

\begin{enumerate}
    \item You will not be asked to prove something completely rigorously but
    learning how to use arguments such as proof by contradictions will help
    you to reason through problems in the exam.

    \item Although you're not directly tested on logic, 
        familiarity with what we have discussed is recommended 
        as mathematics is logical.

    \item Sets:
        \begin{itemize}
            \item Set operations
            \item De Morgan's law for sets
            \item Venn Diagram
        \end{itemize}

    \item Functions:
        \begin{itemize}
            \item Injection, surejection, bijection-- knowing how to recoginize these objects.
            \item Graph-- knowing when a set $G$ is the graph of a function.
            \item Composition
        \end{itemize}

    \item Proof by induction
\end{enumerate}



\end{document}
